SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-26 scipy-1.0/paper.tex
Add a section on the scope of SciPy

\author[1]{Pauli Virtanen}
\author[2,*]{Ralf Gommers}
\author[3,4]{Tyler Reddy}
\author[5]{Anne Archibald}
\author[6]{Andrew Nelson}
\author[7]{Charles Harris}
\author[8]{CJ Carey}
\author[9]{Denis Laxalde}
\author[10]{Eric Larson}
\author[11]{Eric Moore}
\author[12]{Eric Quintero}
\author[13]{Evgeni Burovski}
\author[14]{Jaime Fernández del Río}
\author[15]{Josef Perktold}
\author[16]{Josh Wilson}
\author[17]{Matthew Brett}
\author[18]{Nikolay Mayorov}
\author[19]{Warren Weckesser}
\author[20]{Matt Haberland}
\author[21]{Scott Sievert}
\author[22]{Yu Feng}
\author[23]{Antonio Horta Ribeiro}
\author[24]{Ian Henriksen}

\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[3]{UC Berkeley Institute for Data Science,
          Berkeley, CA, 94720, USA}
\affil[4]{Los Alamos National Laboratory,
	  Theoretical Division 6,
          Los Alamos, NM, 87545, USA}
\affil[5]{Affiliation, department, city, postcode, country}
\affil[6]{Affiliation, department, city, postcode, country}
\affil[7]{Affiliation, department, city, postcode, country}
\affil[8]{Affiliation, department, city, postcode, country}
\affil[9]{Affiliation, department, city, postcode, country}
\affil[10]{Affiliation, department, city, postcode, country}
\affil[11]{Affiliation, department, city, postcode, country}
\affil[12]{Affiliation, department, city, postcode, country}
\affil[13]{Affiliation, department, city, postcode, country}
\affil[14]{Affiliation, department, city, postcode, country}
\affil[15]{Affiliation, department, city, postcode, country}
\affil[16]{Affiliation, department, city, postcode, country}
\affil[17]{Affiliation, department, city, postcode, country}
\affil[18]{Affiliation, department, city, postcode, country}
\affil[19]{Affiliation, department, city, postcode, country}
\affil[20]{Affiliation, department, city, postcode, country}
\affil[21]{Affiliation, department, city, postcode, country}
\affil[22]{Affiliation, department, city, postcode, country}
\affil[23]{Affiliation, department, city, postcode, country}
\affil[24]{University of Texas at Austin,
           Instite for Computational Engineering and Sciences,
	   Austin, TX, 78712, USA}

@@

\textbf{Project scope}
SciPy aims to provide fundamental algorithms for scientific computing. The
breadth of its scope was derived from the Guide to Available Mathematical
Software classification system (GAMS\cite{boisvert1991guide}). In areas
that move relatively slowly, e.g. linear algebra, SciPy aims to provide
complete coverage. In other areas it aims to provide fundamental building
blocks while interacting well with other packages specialized in that area.
For example, SciPy provides what one expect to find in a
statistics textbook (probability distributions, hypothesis tests, frequency
statistics, correlation functions, and more), while Statsmodels provides
more advanced statistical estimators and inference methods, scikit-learn
covers machine learning, PyMC3, emcee and PyStan cover Bayesian statistics
and probabilistic modelling.

We use the following criteria to determine whether or not to include new
functionality in SciPy:
\begin{itemize}
    \item The algorithm is of relevance to multiple fields of science.
    \item The algorithm is demonstrably important.  E.g., it is classic
    enough to be included in textbooks, or it is based on a peer-reviewed article
    which has a significant number of citations.
\end{itemize}

@@

When writing algorithms or wrappers in Cython, it is often convenient to call directly into the libraries that SciPy wraps rather than routing the call back through the Python interpreter.
SciPy currently includes Cython wrappers for many BLAS and LAPACK routines and for many of the special functions provided in the \texttt{scipy.{\allowbreak}special} submodule.
These wrappers are available in the modules \texttt{scipy.{\allowbreak}linalg.{\allowbreak}cython\_blas}, \texttt{scipy.{\allowbreak}linalg.{\allowbreak}cython\_lapack}, and \texttt{scipy.{\allowbreak}special.{\allowbreak}cython\_special} respectively.
The low-level interfaces for Cython can also be used by third party libraries to get direct access to the functions in these libraries while avoiding the overhead of Python function calls{\textemdash}this can give performance gains of one or two orders of magnitude for many use cases.
Cython's cimport machinery allows Cython based modules to share C-level objects with other Cython modules without requiring that the third-party extensions link against any additional libraries.
Function pointers to wrappers for library routines can also be shared in this way, so that Cython modules using the interface provided by SciPy no longer have to worry about finding and linking against the original library.
This lets other extensions avoid the complexity of finding and using the correct libraries on the various possible Fortran compiler ABI and OS combinations.
The low-level Cython wrappers provide an OS and Fortran compiler independent interface for the libraries they wrap.

To help with both correctness and ease of maintenance, most of these low-level Cython wrappers are generated automatically.
The wrappers for BLAS and LAPACK are primarily generated using type information that is parsed from the BLAS and LAPACK source files using f2py, though a small number of routines use hand-written type signatures instead.
The input and output types of each routine are saved in a data file that is read at build time and used to generate the corresponding Cython wrapper files.
The wrappers in \texttt{scipy.{\allowbreak}special.{\allowbreak}cython\_special} are also generated from a data file containing type information for the wrapped routines.

@@

\subsection*{Statistical distributions}
The \texttt{scipy.stats} module provides provides more than 100 probability
distributions and a framework to implement additional distributions. Given
an expression for a probability distribution function (pdf),
the framework will calculate moments, cumulative distribution function (cdf),
differential entropy, and more. Those properties are calculated based on
generic code, e.g., numerical integration of the pdf to obtain the cdf.
Where possible, the generic code is replaced by explicit formulas or more
accurate or efficient implementations. For example, most distributions have
an explicit formula for the cdf, so it is used instead of integrating the
pdf. The distributions framework also allows the user to draw random
variates from the distribution. Drawing random variates now accepts a \texttt{random\_state}
parameter, which is either a \texttt{numpy.random.RandomState} object or an
integer used to generate such an object, to provide fine-grained user-level
control over the random state of a workflow.
Currently about 80 continuous univariate distributions, 12 discrete univariate
distributions and 10 multivariate distributions are implemented.
Key recent distributions added to \texttt{scipy.stats} include the histogram-based
distribution in \texttt{scipy.stats.rv\_histogram} and the multinomial
distribution in \texttt{scipy.stats.multinomial} (used, for example, in natural
language processing\cite{Griffiths5228}). \texttt{multinomial} is the first and so 
far the only multivariate discrete distribution available in SciPy.

@@

\textbf{Maintainers and contributors}
The SciPy project has approximately 15 active maintainers - people who review
others' contributions, and in general do everything needed to ensure that
the software and the project move forward. Maintainers are critical to the
health of the project\cite{eghbal2016}; their skills and efforts largely
determine how fast the project moves forward, and they enable contributions
from a much larger group. Accordingly, the project also has an additional
~100 unique contributors for every 6-monthly release cycle. Anyone with the
interest and skills can become a contributor or maintainer; the SciPy
Developer Guide provides guidance on how to do that.

>>>>

\author[1]{Pauli Virtanen}
\author[2,*]{Ralf Gommers}
\author[3,4]{Tyler Reddy}
\author[5]{Anne Archibald}
\author[6]{Andrew Nelson}
\author[7]{Charles Harris}
\author[8]{CJ Carey}
\author[9]{Denis Laxalde}
\author[10]{Eric Larson}
\author[11]{Eric Moore}
\author[12]{Eric Quintero}
\author[13]{Evgeni Burovski}
\author[14]{Jaime Fernández del Río}
\author[15]{Josef Perktold}
\author[16]{Josh Wilson}
\author[17]{Matthew Brett}
\author[18]{Nikolay Mayorov}
\author[19]{Warren Weckesser}
\author[20]{Matt Haberland}
\author[21]{Scott Sievert}
\author[22]{Yu Feng}
\author[23]{Antonio Horta Ribeiro}

\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[3]{UC Berkeley Institute for Data Science,
          Berkeley, CA, 94720, USA}
\affil[4]{Los Alamos National Laboratory,
	  Theoretical Division 6,
          Los Alamos, NM, 87545, USA}
\affil[5]{Affiliation, department, city, postcode, country}
\affil[6]{Affiliation, department, city, postcode, country}
\affil[7]{Affiliation, department, city, postcode, country}
\affil[8]{Affiliation, department, city, postcode, country}
\affil[9]{Affiliation, department, city, postcode, country}
\affil[10]{Affiliation, department, city, postcode, country}
\affil[11]{Affiliation, department, city, postcode, country}
\affil[12]{Affiliation, department, city, postcode, country}
\affil[13]{Affiliation, department, city, postcode, country}
\affil[14]{Affiliation, department, city, postcode, country}
\affil[15]{Affiliation, department, city, postcode, country}
\affil[16]{Affiliation, department, city, postcode, country}
\affil[17]{Affiliation, department, city, postcode, country}
\affil[18]{Affiliation, department, city, postcode, country}
\affil[19]{Affiliation, department, city, postcode, country}
\affil[20]{Affiliation, department, city, postcode, country}
\affil[21]{Affiliation, department, city, postcode, country}
\affil[22]{Affiliation, department, city, postcode, country}
\affil[23]{Affiliation, department, city, postcode, country}

@@

\textbf{Project scope}
SciPy aims to provide fundamental algorithms for scientific computing. The
breadth of its scope was derived from the Guide to Available Mathematical
Software classification system (GAMS\cite{boisvert1991guide}). In areas
that move relatively slowly, e.g. linear algebra, SciPy aims to provide
complete coverage. In other areas it aims to provide fundamental building
blocks, while interacting well with other packages specialized in that area.
For example for statistics, SciPy provides what one expect to find in a
statistics textbook (probability distributions, hypothesis tests, frequency
statistics, correlation functions, and more), while Statsmodels provides
more advanced statistical estimators and inference methods, scikit-learn
covers machine learning, PyMC3, emcee and PyStan cover Bayesian statistics
and probabilistic modelling.

We use the following criteria to determine whether or not to include new
functionality in SciPy:
\begin{itemize}
    \item The algorithm is of relevance to multiple fields of science.
    \item The implementation is demonstrably important.  E.g., it is classic
    enough to be included in textbooks, or it is based on a peer-reviewed article
    which has a significant number of citations.
\end{itemize}

@@

@@

\subsection*{Statistical distributions}

@@

\textbf{Maintainers and contributors}
The SciPy project has approximately 15 active maintainers (people who review
others' contributions, and in general do everything needed to ensure that
the software and the project move forward).  It also has an additional ~100
unique contributors for every 6-monthly release cycle.  Maintainers are
critical to the health of the project\cite{eghbal2016}; they enable contributions
from a much larger group, and their skills and efforts largely determine how
fast the project moves forward.  Anyone with the interest and skills can become
a maintainer; the SciPy Developer Guide provides guidance on how to do that.
